Two-component thermal dust emission model: application to the {\it PLANCK} HFI maps

### 2014-01-22 ms.tex
clean up of pixelization subsection

The \PLANCK~217 GHz and 353 GHz data are provided in thermodynamic $\delta T$, 
while \verb|i100| and the higher frequency \PLANCK~maps are provided in units 
of MJy/sr. Although the aforementioned preprocessing steps were conducted with 
each map in its native units, we converted the 217 GHz and 353 GHz 
measurements to MJy/sr according to \cite{planckresponse} prior to performing 
SED fits.

@@

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into independent pixels of 
angular size $\sim$1.72$'$, defined by the HEALPix pixelization with nside=2048
\citep{healpix}. This is convenient because the Planck maps are provided in 
this format and this pixelization adequately samples the $6.1'$ resolution maps
under consideration. We reiterate that each pixel is fit independently of 
neighboring pixels.

%mention that we're using healpix in Galactic coordinates !!!!!!

>>>>

The \PLANCK~217 GHz and 353 GHz data are provided in units of thermodynamic 
$\delta T$, while \verb|i100| and the higher frequency \PLANCK~maps are 
provided in units of MJy/sr. Although the aforementioned preprocessing steps 
were conducted with each map in its native units, we converted the 217 GHz and 
353 GHz measurements to MJy/sr according to \cite{planckresponse} prior to 
performing SED fits.

@@

% sentence here summarizing what the following subsections will describe ?

\subsection{Pixelization}
\label{sec:pix}
For the purpose of fitting, we break the sky into $\sim$50 million 
non-overlapping pixels of angular size $\sim$1.72$'$, defined by the HEALPix 
pixelization in Galactic coordinates, with $N_{side}$=2048 \citep{healpix}. 
This pixelization is convenient because it is the same format in which the 
\PLANCK~HFI maps were released, and because it adequately samples the $6.1'$ 
resolution maps under consideration. Our procedure will fit the intensity 
measurements in each spatial pixel independently of those in neighboring 
pixels.
